Dark matter web in the Universe

### 2018-06-18 Draft/thesis-ku.tex
acknow

So many people to thank here ---

>>>>

I would like to express my deepest gratitute to my adviser Prof. Sergei Shandarin, who has been my source of invaluable advice, encouragement and motivation from the first day of graduate school. Sergei has not only been instrumental in shaping this dissertation, but has also helped me grow as a physicist. His passion for intellectual pursuit and critical thinking will always be my inspiration.

I would also like to thank my thesis committee: Prof. Hume Feldman, Prof. Bruce Twarog, Prof. Barbara Anthony-Twarog, Dr. Suzanne Shontz, Prof. Mikhail Medvedev for supervision and guidance that has been important for the materialisation of this thesis.

My appreciation to the friendly staff and faculty at the Department of Physics and Astronomy, especially Dr. Jennifer Delgado, Kristin Rennells, Kim Hubbel and Joel Saurwein for being kind, supportive and patient with me.

It has been a great pleasure sharing office with Brett, Alex, Yuyu and Keita over the past few years. Stimulating conversations -- physics or otherwise -- was always fun and exciting. Special thanks to Donald and Sinan for the company that kept me sane over the course of PhD.

My time at Lawrence was enjoyable in large part due to many wonderful people I was surrounded by. I've had amazing roommates: Niranjan, Niharika, Darshan and Charu, who

Thank you Mum and Dad, for unconditional love and support throughout graduate school and my life in general.
